Reply To Examiners

### 2014-05-08 answer_thesis_examiner/chap1.tex
auto

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections \& Comments} \\
 \hline
 \endhead
15 & 6 & missing explaination for $\vec{E},B$ & explaination added \\
15 & 12 & x,y plane & x \& y planes \\
15 & -2 & $2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi)$ & $2 \frac{\xi_x(t) \xi_y(t)}{E_x^0 E_y^0} \cos (\Delta \phi)$ \\
16 & 2 & The parameters ... are: & The parameters ... are: the intensity orientation angle ($\theta$), the ellipticity angle ($\Psi$) and the orientation angle ($\chi$) \\
17 & 4 & machenics & mechanics \\
17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
20 & -1 & font size for Eqns 2.10 and 2.11 is different from the rest of the thesis & This is due to space restriction, where the matrix representation in the normal font size would require a larger width that that is available in one line \\
33 & -10 & Eqn. [2.15) & Eqn. 2.15 \\
34 & 10 & how did you get this Eqn? & References are added for each Equation \\
35 & 10 & which distribution is more appropriate & The most appropriate distribution is the distribution of the ``true signal'', which of course, is unknown \\
43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\
\end{longtable}    
\rowcolors{1}{white}{}

%In page 14 of the returned thesis, Examiner No. 1 wonders ``Does the intagration of the PDF given for $A_x, A, I$ sum up to 1?''.
%First I would like to thank Examiner No. 2 for raising such a question.
%By going through his question, I realized that a negative sign were missed in the equation for $pdf(A_x)$.
%With that corrected, let me repeat the Equations here
%
%\begin{align}
%pdf(A_x) &= \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
%pdf(A)   &= \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
%pdf(A_1) &= 2A_1 e^{-A_1^2} \\
%pdf(I)   &= \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
%\end{align}
%
%The integration of these becomes
%\begin{align}
%cdf(A_x) &= \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} &= 1 \\
%cdf(A) &= \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} &= 1\\
%cdf(A_1) &= \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} &= 1\\
%cdf(I) &= \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} &= 1
%\end{align}
%
%
%For the first equation, consider the standard PDF equation for normal distribution centering around $\mu$ and having variance $\sigma$ given below
%
%\begin{align}
%\textbf{Normal Distribution: } & pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}} \\
%\textbf{Chi-Squared Distribution (dof=2): } & pdf(x) = \frac{e^{-x/2}}{2} \\ %pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}} \\
%\textbf{Exponential Distribution: } & pdf(x) = \lambda e^{- \lambda x}
%\end{align}
%
%\begin{align}
%\textbf{Normal Distribution: } & cdf(x) = \frac{1}{2} \left[ 1 + erf \left( \frac{x-\mu}{\sqrt{2\sigma^2}} \right) \right] \\
%\textbf{Chi-Squared Distribution (dof=2): } & cdf(x) = 1 - e^{-x/2}\\
%\textbf{Exponential Distribution: } & cdf(x) = 1 - e^{- \lambda x}
%\end{align}
%
%Clearly, $A_x$ follows the normal distribution with expectation $avg(A_x)=0$ and variance $var(A_x)=\frac{\sigma}{\sqrt{2}}$.
%
%Next consider the standard PDF equation for chi-square distribution with $k$ degree of freedom given below:
%
%\begin{align}
%pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}}
%\end{align}
%
%Set $k=2$, and thus $\Gamma(k/2)=\Gamma(1)=1$, then:
%
%\begin{align}
%pdf(x) = \frac{e^{-x/2}}{2} 
%\end{align}
%
%Set $\frac{x}{2} = \frac{A^2}{\sigma^2}$ or $x = \frac{2A^2}{\sigma^2}$, thus $\frac{dx}{dA} = \frac{4A}{\sigma^2}$.
%Variable change theorem give us:
%
%\begin{align}
%pdf(A) = \frac{e^{-A^2/\sigma^2}}{2} \frac{4A}{\sigma^2} = \frac{2A}{\sigma^2} e^{-\frac{A^2}{\sigma^2}}
%\end{align}
%
%
%For the $pdf(I)$, if we set $\lambda = \frac{1}{\sigma^2}$ then the equation turns out to be the standard PDF equation for the Exponential Distribution 
%
%\begin{align}
%pdf(x) = \lambda e^{- \lambda x}
%\end{align}

>>>>

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections \& Comments} \\
 \hline
 \endhead
15 & 6 & missing explaination for $\vec{E},B$ & explaination added \\
15 & 12 & x,y plane & x \& y planes \\
15 & -2 & $2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi)$ & $2 \frac{\xi_x(t) \xi_y(t)}{E_x^0 E_y^0} \cos (\Delta \phi)$ \\
16 & 2 & The parameters ... are: & The parameters ... are: the intensity orientation angle ($\theta$), the ellipticity angle ($\Psi$) and the orientation angle ($\chi$) \\
17 & 4 & machenics & mechanics \\
17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
20 & -1 & font size for Eqns 2.10 and 2.11 is different from the rest of the thesis & This is due to space restriction, where the matrix representation in the normal font size would require a larger width that that is available in one line \\
33 & -10 & Eqn. [2.15) & Eqn. 2.15 \\
34 & 10 & how did you get this Eqn? & References are added for each Equation \\
35 & 10 & which distribution is more appropriate & The most appropriate distribution is the distribution of the ``true signal'', which of course, is unknown \\
43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\
76 & -4 & chapter 2 & Chapter 2 \\
129 & 1 & cahpter 5 & Chapter 5 \\
129 & 6 & theoretical results & theoretical contributions \\
129 & 21 & this thesis unite & this thesis unites \\
130 & 1 & articles that has been & articles that have been \\
132 & 14 & an important benefits & several important benefits \\
\end{longtable}    
\rowcolors{1}{white}{}
